A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
Added list of wikipedia langauges

% Anonymized for submission
\author{}

@@

@@

The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.  In total, XXXXXX translation tasks were completed by YYYY workers over a period of ZZZ months.

>>>>

% Anonymized for submission
%\author{}

@@

\begin{table}[htdp]
\scriptsize 
\begin{center}
\begin{tabular}{|p{0.95\linewidth}|}
\hline
{\sc 500k+ articles:}
Dutch (nl), English (en), French (fr), German (de), Italian (it), Japanese (ja), Polish (pl), Portuguese (pt), Russian (ru), Spanish (es)\\
\hline
{\sc 100k-500k articles:} Arabic (ar), Basque (eu), Bulgarian (bg), Catalan (ca), Chinese (zh), Croatian (hr), Czech (cs), Danish (da), Esperanto (eo), Finnish (fi), Hebrew (he), Hindi (hi), Hungarian (hu), Indonesian (id), Kazakh (kk), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Persian (fa), Romanian (ro), Serbian (sr), Slovak (sk), Slovenian (sl), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war)\\
\hline
{\sc 10k-100k articles:}
Azerbaijani (az), Afrikaans (af), Albanian (sq), Amharic (am), Aragonese (an), Armenian (hy), Asturian (ast), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Bosnian (bs), Breton (br), Cebuano (ceb), Galician (gl), Georgian (ka), Greek (el), Gujarati (gu), Haitian (ht), Icelandic (is), Ido (io), Irish (ga), Javanese (jv), Kannada (kn), Kurdish (ku), Latvian (lv), Low Saxon (nds), Luxembourgish (lb), Macedonian (mk), Malagasy (mg), Malayalam (ml), Marathi (mr), Neapolitan (nap), Nepali (ne), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Quechua (qu), Serbo-Croatian (sh), Sicilian (scn), Sundanese (su), Swahili (sw), Tagalog (tl), Tamil (ta), Tatar (tt), Telugu (te), Thai (th), Urdu (ur), Walloon (wa), Welsh (cy), West Frisian (fy), Yoruba (yo), Zazaki (diq)\\
\hline
{\sc $<$10k articles:} Central Bicolano (bcl), Ilokano (ilo), Kapampangan (pam), Pashto (ps), Punjabi (pa), Sindhi (sd), Somali (so), Tibetan (bo), Uzbek (uz), Wolof (wo)\\
\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures in this paper.}\label{wikipedia-buckets}
\end{table}%

@@

The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.  In total, 308079 translation tasks were completed by 5271 workers over
a period of three and a half months.
20955 synonym tasks were used to judge the submitted translations, and
were completed by an additional 1006 workers.
